%%
% BIThesis 本科毕业设计论文模板（全英文） —— 使用 XeLaTeX 编译 The BIThesis Template for Undergraduate Thesis
% This file has no copyright assigned and is placed in the Public Domain.
%%

\begin{acknowledgements}
The completion of this thesis would not have been possible without the guidance, help, and support of many people. First, I would like to express my sincere gratitude to my university supervisor, Prof. Jinhui Pang, for her guidance throughout my graduation project. From the selection of the research topic and the clarification of the research ideas to the adjustment of the thesis structure and the revision of the manuscript, Prof. Pang provided patient support and valuable suggestions. Her guidance helped me gradually identify the focus of the work and complete the thesis.

I am also grateful to my external supervisor, Ms. Haitao Zhang, for her guidance and support in the practical and engineering aspects of this project. Her advice helped me gain a clearer understanding of the application background of multimodal target fusion and behavior analysis systems. I would also like to thank my former mentor, Sijie Ruan, who introduced me to research and helped me take the first steps in academic exploration. During the research and implementation process, Zhuoyi Yang also provided direct and detailed assistance in technical discussions, experimental progress, and thesis improvement. I would like to express my sincere thanks to him as well.

In addition, I would like to thank BIT and all the teachers in the School for their instruction during my undergraduate study. Their teaching helped me build the professional foundation and engineering ability required for this project. I am also grateful to XYC, where I met many interesting and inspiring people and learned from their enthusiasm, curiosity, and collaboration. I also thank Yichun Yang, Yi Liu, and my other classmates and friends for their help in literature search, technical discussion, study, and thesis revision. Finally, I am deeply grateful to my family for their constant understanding and support in my study and daily life. Due to my limited ability and experience, this thesis may still contain shortcomings, and I sincerely welcome criticism and corrections from the teachers.
\end{acknowledgements}
